---
title: "Methods & Techniques"
format: html
---

This section provides a structured overview of methods and techniques for urban morphology analysis. All methods and techniques described here are cross-referenced with the Examples part of the book.

## Methods
```{r}
library(leaflet)
library(leaflet.extras)

# load maps
map2 <- leaflet() %>%
  setView(lng = 4.4777, lat = 51.9244, zoom = 13) %>%
  addTiles() %>%  # Base OSM layer
  addTiles(
    urlTemplate = "https://allmaps.xyz/maps/8ebee9ef638a08cf/{z}/{x}/{y}.png",
    attribution = "Allmaps",
    options = tileOptions(opacity = 0.7)  # Optional: make it semi-transparent
  ) |> 
  addFullscreenControl()
map2
```



### Typo-morphology analysis

### Space syntax analysis
```{r space-syntax, echo=FALSE}
question("Which one is the most suitable analysis method if you want to find the settlement centers in a larger region?",
  answer("Angular Integration, 800m"),
  answer("Angular Integration, 1500m", correct = TRUE),
  answer("Angular Choice, 800m", message = "Angular choice measures the through-movement potential."),
  answer("Angular Choice, 1500m", message = "Angular choice measures the through-movement potential.")
)
```


### (Morpho-)Typology analysis

## Techniques

### Calculating density

### Figure-ground mapping

### Mapping spatial structures
```{r}
#| label: leaflet-limburg
#| echo: false
#| message: false
#| warning: false

library(leaflet)
library(sf)
library(here)

railway <- st_read(here("data-for-map/limburg_railway.gpkg")) |> st_transform(4326)
water <- st_read(here("data-for-map/limburg_water.gpkg")) |> st_transform(4326)
industry <- st_read(here("data-for-map/limburg_industry.gpkg")) |> st_transform(4326)

leaflet() |>
  addProviderTiles("CartoDB.Positron") |>
  setView(lng = 5.85, lat = 51.25, zoom = 13) |>  # Limburg coordinates
  addPolylines(
    data = water,
    color = "darkblue",
    weight = 1.5,
    opacity = 1,
    group = "Water",
    popup = ~paste("name:", ifelse(!is.na(name), name, "N/A"))
  ) |>
  addPolylines(
    data = railway,
    color = "darkred",
    weight = 0.8,
    opacity = 1,
    group = "Railways",
    dashArray = "10, 5",
    popup = ~paste("name:", ifelse(!is.na(name), name, "N/A"))
  ) |>
  addPolygons(
    data = industry,
    color = "gray30",
    weight = 1,
    opacity = 1,
    fillOpacity = 0.8,
    group = "Industry",
    popup = ~paste("name:", ifelse(!is.na(name), name, "N/A"))
  ) |>
  addScaleBar(position = "bottomleft") |>
  addMiniMap(toggleDisplay = TRUE) |>
  addLayersControl(
    baseGroups = c("Base Map"),
    overlayGroups = c("Railways", "Water", "Industry"),
    options = layersControlOptions(collapsed = FALSE)
  )

```

